---
title: "EDA on Amazon Books"
description: "I will be utilizing my skills in ggplot and showing you some of the things I can do in R"
type: post
date: 2022-03-06
tags: ["ggplot", "R"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, results = 'hide', include=FALSE}
library(tidyverse)
library(readr)
library(ggridges)
```

```{r, results='hide', include=FALSE}
books <- read_csv(file = "bestsellers.csv")
```

## Data

The data I have loaded in is called Amazon's Top 50 Selling Books from 2009-2019. Here is a look at the data.

```{r, echo=FALSE}
glimpse(books)
summary(books)
```

## Visualizations

Lets take a look at the prices of the books according to genre.

```{r, echo=FALSE}
ggplot(books, aes(
  x = Price,
  fill = Genre
)) +
  geom_density(
    adjust = 2,
    alpha = 0.5
  ) +
  labs(
    x = "Price",
    y = "Density",
    title = "Price",
    fill = "Genre"
  )
```

The graph above looks like they sell the books for about the same price. Now we will take a look at the relationship between User Rating and Genre.

```{r, echo=FALSE}
ggplot(books, aes(
  x = `User Rating`,
  fill = Genre 
)) +
  geom_bar(
  ) 
```

```{r, echo=FALSE}
ggplot(books, aes(
  x = `User Rating`,
  fill = Genre
)) +
  geom_bar(
    position="fill"
  ) 
```

```{r}
ggplot(books, aes(
  x= Price,
  y = Genre,
  fill= Genre, 
  color=Genre)) +
  geom_density_ridges(alpha = 0.5)
```

## Data Arranging

Lets take a look at the highest ratings in the dataset, the authors with 4.9 and above. 

```{r, echo=FALSE}
top <- books %>%
  filter(
    `User Rating` >= 4.9
  ) %>%
  select(Author, `User Rating`, Reviews)
top
```
We will take a look at who has the most highest rated books and no surprise it is Dr. Seuss.
```{r, echo=FALSE}
top %>%
  count(Author) %>%
  arrange(desc(n))
```

I am also curious to see who has the most books in the top 50, so let's take a look at that.

```{r, echo=FALSE}
books %>%
  count(Author) %>%
  arrange(desc(n))
```

We can see the more popular authors from reviews.

```{r}
ggplot(top, aes(
  y = Author,
  fill = Reviews)) +
  geom_bar(position = "fill") +
  labs(
    x = "Proportion",
    y = "Author",
    fill = "Review",
    title = "Review Frequency of Top Authors"
  )
```



